Scheduling Musical Events in Max/MSP with Scheme For Max

### 2021-08-11 paper-1/paper-1.tex
edits

%%
%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall, anonymous, review]{acmart}
%% NOTE that a single column version is required for 
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to 
%% \documentclass[manuscript,screen]{acmart}
%% 
%% To ensure 100% compatibility, please check the white list of
%% approved LaTeX packages to be used with the Master Article Template at
%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
%% before creating your document. The white list page provides 
%% information on how to submit additional LaTeX packages for 
%% review and adoption.
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Iain C.T. Duncan}
%%\authornote{Both authors contributed equally to this research.}
\email{iainctduncan@gmail.com}
\affiliation{
  \institution{University of Victoria}
  \streetaddress{}
  \city{Victoria}
  \state{BC}
  \country{Canada}
  \postcode{}
}

@@

Future plans for the project include a version for the open-source
Pure Data platform, similar to Max in many ways and created also by Miller Puckette,
the original author of Max. \textbf{Scheme For Pure Data} is now in beta release, available
as source code, with binary releases planned for August 2021. In addition
to this, experimental work on running Scheme for control-rate DSP is planned.
This would entail Scheme executing in the timed audio rendering thread, but
at a subdivision of the audio sample rate such as every 32 or 64 samples, 
thus generating streams similar to the way digital audio is rendered, but
at a lower resolution suitable for use as signal modulators. (The ability
to run DSP code at a lower sample rate for modulator signals is  
is called the "control rate" in CSound and other similar audio programming platforms.)

@@

https://github.com//scheme-for-max
%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
%%\begin{acks}
%%Scheme For Max would not exist without the work of many people. 
%%Bill Schottstaedt created Common Lisp Music and the s7 Scheme implementation,
%%and has been invaluable as a source of advice on s7. Heinrich Taube
%%created Common Music and has been an inspiration through his seminal book
%%on algorithmic composition with Lisp, "Notes from the Metalevel".
%%Luigi Castelli and Alex Harker helped with programming questions
%%and build assistance. 
%%S4M of course depends on Max and thus owes a huge debt to 
%%Miller Puckette and David Zicarelli. And finally, Andrew Schloss has
%%been a source of encouragement and support through the years of 
%%exploration that led to the Scheme For Max project.
%%
%%\end{acks}

>>>>

%%
%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall]{acmart}
%% NOTE that a single column version is required for 
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to 
%% \documentclass[manuscript,screen]{acmart}
%% 
%% To ensure 100% compatibility, please check the white list of
%% approved LaTeX packages to be used with the Master Article Template at
%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
%% before creating your document. The white list page provides 
%% information on how to submit additional LaTeX packages for 
%% review and adoption.
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Iain C.T. Duncan}
%%\authornote{Both authors contributed equally to this research.}
\email{iduncan@uvic.ca}
\affiliation{
  \institution{University of Victoria}
  %%\streetaddress{}
  \city{Victoria}
  \state{BC}
  \country{Canada}
  %%\postcode{V8P 5C2}
}

@@

Future plans for the project include a version for the open-source
Pure Data platform, similar to Max in many ways and created also by Miller Puckette,
the original author of Max. \textbf{Scheme For Pure Data} is now in beta release, available
as source code, with binary releases planned for August 2021. In addition
to this, experimental work on running Scheme for control-rate DSP is planned.
This would entail Scheme executing in the timed audio rendering thread, but
at a subdivision of the audio sample rate such as every 32 or 64 samples, 
thus generating streams similar to the way digital audio is rendered, but
at a lower resolution suitable for use as signal modulators. (The ability
to run DSP code at a lower sample rate for modulator signals 
is called the ``control rate" in CSound and other similar audio programming platforms.)

@@

https://github.com//scheme-for-max
%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
Scheme For Max would not exist without the work of many people. 
Bill Schottstaedt created Common Lisp Music and the s7 Scheme implementation,
and has been invaluable as a source of advice on s7. Heinrich Taube
created Common Music and has been an inspiration through his seminal book
on algorithmic composition with Lisp, "Notes from the Metalevel".
Luigi Castelli and Alex Harker helped with programming questions
and build assistance. 
S4M of course depends on Max and thus owes a huge debt to 
Miller Puckette and David Zicarelli.
George Tzanetakis has assisted with this paper.
And finally, Andrew Schloss has
been a source of encouragement and support through the years of 
exploration that led to the Scheme For Max project.

\end{acks}
